\section{Related Work} \label{sec:related_work}
Several advancements have been made in the field of gender
and age prediction from facial images, utilizing deep learning techniques.
In this section, we present two notable works that have contributed
significantly to the state-of-the-art in this domain.

The work by [Rafique et al., 2019] \cite{rel1} introduces a deep learning
framework based on an ensemble of attentional and residual convolutional
networks with the primary objective of predicting gender and age groups
with a high accuracy rate, treating both features as a classification problem.
The proposed model, trained on the UTKFace dataset,
employs attention mechanisms to focus on
crucial facial regions, enhancing the accuracy of predictions. 
The multi-task learning approach is utilized, and the feature embedding
of the age classifier is augmented with predicted gender information.

In a different approach, [Antipov et al., 2017] \cite{rel2} explores
improvements in existing CNN-based methods for gender and age prediction.
The study investigates key factors that impact the training of
CNNs, including target age encoding, loss function,
CNN depth, pretraining necessity, and training strategy
(mono-task or multi-task).
The authors present state-of-the-art gender recognition and
age estimation models designed according to benchmarks such as
LFW, MORPH-II, and FG-NET.
Notably, their best model won the ChaLearn Apparent Age
Estimation Challenge 2016, significantly
outperforming the solutions of other participants.